\chapter*{List of publications}

\section*{International Journals}
\begin{enumerate}
    \item[J1)] M. Cococcioni, F. Rossi, E. Ruffaldi, S. Saponara and B. Dupont de Dinechin, "Novel Arithmetics in Deep Neural Networks Signal Processing for Autonomous Driving: Challenges and Opportunities," in IEEE Signal Processing Magazine, vol. 38, no. 1, pp. 97-110, Jan. 2021, doi: \url{https://doi.org/10.1109/MSP.2020.2988436}.
    \item[J2)] M. Cococcioni, F. Rossi, E. Ruffaldi, and S. Saponara. "Fast approximations of activation functions in deep neural networks when using posit arithmetic". Sensors 2020, 20(5), 1515; \url{https://doi.org/10.3390/s20051515}.
    \item[J3)] M. Cococcioni, F. Rossi, E. Ruffaldi, and S. Saponara. "Fast deep neural networks for image processing using posits and ARM scalable vector extension". Journal of Real-Time Image Processing 17, 759–771 (2020). \url{https://doi.org/10.1007/s11554-020-00984-x}
    \item[J4)] M. Cococcioni, F. Rossi, E. Ruffaldi and S. Saponara. "Vectorizing posit operations on RISC-V for faster deep neural networks: experiments and comparison with ARM SVE". Neural Comput \& Applic 33, 10575–10585 (2021). \url{https://doi.org/10.1007/s00521-021-05814-0}
    \item[J5)] M. Cococcioni, F. Rossi, E. Ruffaldi and S. Saponara, "A Lightweight Posit Processing Unit for RISC-V Processors in Deep Neural Network Applications," in IEEE Transactions on Emerging Topics in Computing, doi: \url{https://doi.org/10.1109/TETC.2021.3120538}.
  

\end{enumerate}
\section*{International Conferences/Workshops with Peer Review}

\begin{enumerate} 
    \item [C1)] M. Cococcioni, F. Rossi, E. Ruffaldi and S. Saponara (2020). "A Fast Approximation of the Hyperbolic Tangent When Using Posit Numbers and Its Application to Deep Neural Networks". In: Applications in Electronics Pervading Industry, Environment and Society. ApplePies 2019. Lecture Notes in Electrical Engineering, vol 627. Springer, Cham. \url{https://doi.org/10.1007/978-3-030-37277-4_25}
    \item [C2)] M. Cococcioni, F. Rossi, E. Ruffaldi and S. Saponara, "Novel Arithmetics to Accelerate Machine Learning Classifiers in Autonomous Driving Applications," 2019 26th IEEE International Conference on Electronics, Circuits and Systems (ICECS), 2019, pp. 779-782, doi: \url{https://doi.org/10.1109/ICECS46596.2019.8965031}.
    \item [C3)] M. Cococcioni, F. Rossi, E. Ruffaldi and S. Saponara, "A Novel Posit-based Fast Approximation of ELU Activation Function for Deep Neural Networks," 2020 IEEE International Conference on Smart Computing (SMARTCOMP), 2020, pp. 244-246, doi: \url{10.1109/SMARTCOMP50058.2020.00053}.
    \item [C4)] M. Cococcioni, F. Rossi, E. Ruffaldi, S. Saponara, "Faster deep neural network image processing by using vectorized posit operations on a RISC-V processor," Proc. SPIE 11736, Real-Time Image Processing and Deep Learning 2021, 1173604 (12 April 2021); \url{https://doi.org/10.1117/12.2586565}
    \item [C5)] M. Cococcioni, F. Rossi, E. Ruffaldi and S. Saponara (2022). "Experimental Results of Vectorized Posit-Based DNNs on a Real ARM SVE High Performance Computing Machine". In: Applications in Electronics Pervading Industry, Environment and Society. ApplePies 2021. Lecture Notes in Electrical Engineering, vol 866. Springer, Cham. \url{https://doi.org/10.1007/978-3-030-95498-7_9}
    \item[C6)] M. Cococcioni,  F. Rossi,  E. Ruffaldi,  and S. Saponara. "Small reals representations for Deep Learning at the edge: a comparison", Next Generation Arithmetic: Third International Conference, CoNGA 2022, Singapore, March 1–3, 2022, Revised Selected Papers \url{https://doi.org/10.1007/978-3-031-09779-9_8}
    \item[C7)] F. Rossi, L. Fiaschi, M. Cococcioni, S. Saponara. Design and FPGA Synthesis of BAN Processing Unit for non-Archimedean Number Crunching, International Conference on Applications in Electronics Pervading Industry, Environment and Society (APPLEPIES 2022), to appear
\end{enumerate}


